The paper on blockchain front-running

### 2018-09-28 frontrunning/Latex/sections/paper.tex
[frontrunning] add 0x review citation

The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface. Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers. 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay. One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each of his orders. The reason for canceling order could be the unprofitability of the order due to price change. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}. This is illustrated in Figure~\ref{fig:MinerFrontrunning}.

>>>>

The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface. Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers. 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay. One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--~\cite{consesnsys0xReview2017}, to prevent such attacks, the user needs to send a transaction to cancel each of his orders. The reason for canceling order could be the unprofitability of the order due to price change. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}. This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
